### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 2 weiter bearbeitet

\begin{eqnarray}
max: 1*x_1+1*x_2 \label{con1}\\ 
2*x_1+x_2 \le 12 \label{con2}\\ 
2*x_1+3*x_2 \le 7 \label{con3}\\ 
-1*x_1+2*x_2 \le 16 \label{con4}\\ 
x_1,x_2 \ge 0 \label{con5}
\end{eqnarray}

@@

\noindent idea of the evening:
Do not assume to only use integers!
Another variant is to define:
\begin{eqnarray*}
	s=\frac{1}{x_1}\\
	t=\frac{1}{x_2}\\ 
\end{eqnarray*}
the result for Z now is 2 and there are infinite many possibilities to get to 2.

@@

P1=(0,3)\\
P2=(2,4)\\
P3=(1,3)\\
P4=(6,0)

>>>>

\begin{eqnarray}
max. 1*x_1+1*x_2 \label{con1}\\ 
s.t. 2*x_1+x_2 \le 12 \label{con2}\\ 
2*x_1+3*x_2 \le 7 \label{con3}\\ 
-1*x_1+2*x_2 \le 16 \label{con4}\\ 
x_1,x_2 \ge 0 \label{con5}
\end{eqnarray}

@@

@@

For the first point $P_1=(0,3)$ we have to set $s = -1$ and $t = 1$. That result in a maximal value 
for (0,3) because we cannot set $x_2$ arbitrary big due to constraint 4. And if we assign a bigger 
value to $x_1$, would decrease the result. Also we would violate constraint 2, if $x_1$ is to big.\\
\\
P2=(2,4)\\
P3=(1,3)\\
\\
\noindent To make $P_4=(6,0)$ the maximum we set $s = 1$ and $t = -1$. We cannot set $x_1$ to a bigger value 
than 6 without violating constraint 1.
